---
title: "R Notebook"
output: pdf_document
---

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(network)
library(ggplot2)
library(dplyr)
library(data.table)
library(RColorBrewer)
```


```{r message=FALSE, warning=FALSE}
# edge_list <- tibble(from = c(1, 1, 1, 
#                              2, 2, 2, 
#                              3, 3, 3, 
#                              4, 4, 4), 
#                     to = c(2, 3, 4, 
#                            1, 3, 4, 
#                            1, 2, 4, 
#                            1, 2, 3), 
#                     contact = c(.9, .8, .2, # transmission probability
#                                 .9, .7, .1, 
#                                 .8, .7, .6, 
#                                 .2, .1, .6))
# node_list <- tibble(id = 1:4)
```

Group size: 1 : 20
Prevalence: 0.001,0.01,0.03,0.05,0.1,0.15

# Create network: nodes, edges, transmission probabilities
```{r}
N <- 6 # group size
# create nodes
nodes <- tibble(id = 1:N)

# Create edges 
from <- rep(1:N, each = (N-1))
to <- unlist(lapply(1:N, function(x) setdiff(1:N, x)))

# generate matrix of random transmission probabilities 
d = -1
while(d<1e-3){
  Sigma <- matrix(runif(N^2, 0.1, 0.9), nrow = N, ncol = N) # generate random values from .1 to 0.9
  Sigma = 0.5 * (Sigma + t(Sigma)) # make matrix symmetrical 
  diag(Sigma)= rep(1,N) # 1's on diagonal 
  d = det(Sigma)
}

transmission_prob <- as.vector(Sigma)[Sigma != 1] # list of transmission probabilities, removing diagonals

edges <- as.data.frame(cbind(from, to, transmission_prob)) 
```


```{r}
n <- 100 # number of repetitions of simulation
infector <- numeric(n)
infected <- matrix(nrow = n, ncol = N)
dimnames(infected) <- list(1:n, c(1:N))
v_long <- rep(1:10, each = 2)
v <- v_long[1:N]
prev <- 0.01
risk_probs <- prev*v
# risk_probs <- c(.8, .1, .02, .03, .05)
# category zero is probability that noone gets infected
# Prevalence: 0.001,0.01,0.03,0.05,0.1,0.15

#infect_start <- rmultinom(n, size = 1, prob=c(0.6, 0.05, 0.2, .15))
# choose who is infected:
# each individual has different risk (prob); repeatedly (n=100) choose size = 1 individual to be infected

for (i in 1:n){
  # choose starting infected individual
  # infector[i] <- which(rmultinom(1, size = 1, prob=risk_probs) > 0) - 1
  # record who was infected; 0 if nobody infected
  flip <- rbinom(1, 1, prob = (1-exp(sum(log(1-risk_probs)))))

  if (flip == 0) { # nobody infected
    infected[i,] <- 0
  } 
  else{ # transmit infection
    infector[i] <- which(rmultinom(1, size = 1, prob= (v/sum(v))) > 0) 
    infected[i,infector[i]] <- 1 # infector 
    infect_contact <- edges[edges$from == infector[i],] 
    infected[i,-infector[i]] <- unlist(lapply(infect_contact$transmission_prob, function(x) x > runif(1, min = 0, max = 1)))
    # infected if contact rate > uniform(0,1)
  }
}

group_size <- rep(N, n)
dat <- cbind(infector, infected, group_size)

# store probability of sum(x)=k positives for given group size
probs <- matrix(nrow = (N+1), ncol = N) # columns = group size, rows = number positives (0: group size)
dimnames(probs) <- list(0:N, 1:N)
probs[,N] <- unlist(lapply(0:N, function(x) sum(rowSums(infected) == x)/n))

```

distribution of the sum of number of infected people
expected sensitivity of test 

p(sum(x) = 1) = 
p (sum(x) = 2) = 
p(sum(x) = 3) = 

p(sum(x) = k | prevalence)

# adapt to loop over different group sizes
This loop also simulates the probability that someone becomes infected at all 
```{r}
group_max <- 20 # maximum group size
n <- 10000 # number of repetitions of simulation

# fxn to calculate p(k positives | group size, prevalence)
calc_probs <- function(N, prev){ # N = group size, prev = prevalence

  # create nodes
  nodes <- tibble(id = 1:N)
  
  # Create edges 
  from <- rep(1:N, each = (N-1))
  to <- unlist(lapply(1:N, function(x) setdiff(1:N, x)))
  
  # generate matrix of random transmission probabilities 
  # replace with values from the literature 
  d = -1
  while(d<1e-3){
    Sigma <- matrix(runif(N^2, 0.1, 0.9), nrow = N, ncol = N) # generate random values from .1 to 0.9
    Sigma = 0.5 * (Sigma + t(Sigma)) # make matrix symmetrical 
    diag(Sigma)= rep(1,N) # 1's on diagonal 
    d = det(Sigma)
  }
  
  transmission_prob <- as.vector(Sigma)[Sigma != 1] # list of transmission probabilities, removing diagonals
  
  edges <- as.data.frame(cbind(from, to, transmission_prob)) 
  
  infector <- numeric(n)
  infected <- matrix(nrow = n, ncol = N)
  dimnames(infected) <- list(1:n, c(1:N))
  v_long <- rep(1:10, each = 2)
  v <- v_long[1:N]
  # prev <- 0.01
  risk_probs <- prev*v
  
  for (i in 1:n){
    
    # flip coin to decide if anyone is infected
    flip <- rbinom(1, 1, prob = (1-exp(sum(log(1-risk_probs)))))
    # remove this line - assume someone is infected 
    
    if (flip == 0) { # nobody infected
      infected[i,] <- 0
    } 
    else{ # flip = 1 -> transmit infection
      infector[i] <- which(rmultinom(1, size = 1, prob= (v/sum(v))) > 0) 
      infected[i,infector[i]] <- 1 # infector 
      infect_contact <- edges[edges$from == infector[i],] 
      infected[i,-infector[i]] <- unlist(lapply(infect_contact$transmission_prob, function(x) x > runif(1, min = 0, max = 1)))
      # infected if contact rate > uniform(0,1)
    }
  }
  
  # store probability of sum(x)=k positives for given group size
  probs <- c(unlist(lapply(0:N, function(x) sum(rowSums(infected) == x)/n)), rep(0, group_max - N))
  return(probs)
}

results_prev_01 <- matrix(unlist(lapply(1:20, calc_probs, prev = 0.01)), nrow = (group_max + 1), ncol = group_max)
dimnames(results_prev_01) <- list(0:group_max, 1:group_max) # rows = number positives (0: group size), columns = group size

```

GIVEN that there is an infected individual in the network, what is the probability that other people are infected? 
Simulating propagation through household given there is an infected individual
```{r}
group_max <- 20 # maximum group size
n <- 100000 # number of repetitions of simulation

# fxn to calculate p(k positives | group size, prevalence)
calc_probs <- function(N, min, max){ # N = group size, prev = prevalence
  # create nodes
  nodes <- tibble(id = 1:N)
  
  # Create edges 
  from <- rep(1:N, each = (N-1))
  to <- unlist(lapply(1:N, function(x) setdiff(1:N, x)))
  
  
  infector <- numeric(n) # initial infectious individual in network
  infected <- matrix(nrow = n, ncol = (N-1)) # secondary infected individuals
  dimnames(infected) <- list(1:n, c(1:(N-1)))
  
  for (i in 1:n){
  # generate matrix of transmission probabilities 
  # household transmission- based on literature: 
  # Secondary infection rate = 53% (95% confidence interval [CI] = 46%–60%)
  Sigma <- matrix(runif(N^2, min, max), nrow = N, ncol = N) # generate random values from .1 to 0.9
  Sigma = 0.5 * (Sigma + t(Sigma)) # make matrix symmetrical 
  diag(Sigma)= rep(1,N) # 1's on diagonal 
  
  transmission_prob <- as.vector(Sigma)[Sigma != 1] # list of transmission probabilities, removing diagonals
  
  edges <- as.data.frame(cbind(from, to, transmission_prob)) 
    # choose starting infected individual
    infector[i] <- sample(nodes$id, 1)
    # infected[i,infector[i]] <- 1 # infector 
    infect_contact <- edges[edges$from == infector[i],] 
    infected[i,] <- unlist(lapply(infect_contact$transmission_prob, function(x) x > runif(1, min = 0, max = 1)))
      # infected if contact rate > uniform(0,1)
    }
  
  # store probability of sum(x)=k positives for given group size
  probs <- c(unlist(lapply(0:(N-1), function(x) sum(rowSums(infected) == x)/n)), rep(0, group_max - N))
  return(probs)
}

```

```{r}
sim_probs_house <- matrix(unlist(lapply(2:20, calc_probs, min = 0.4, max= 0.6)), nrow = (group_max), ncol = (group_max-1))
dimnames(sim_probs_house) <- list(1:group_max, 2:group_max) 
# rows = total number of infections (1: (group size)), columns = group size

write.csv(sim_probs_house,"sim_probs_house.csv")
```

```{r}
sim_probs_.1.2 <- matrix(unlist(lapply(2:20, calc_probs, min = 0.1, max= 0.2)), nrow = (group_max), ncol = (group_max-1))
dimnames(sim_probs_.1.2) <- list(1:group_max, 2:group_max) 
# rows = total number of infections (1: (group size)), columns = group size

write.csv(sim_probs_.1.2,"sim_probs_.1.2.csv")
```


```{r}
# routes_network <- network(edge_list, vertex.attr = node_list, matrix.type = "edgelist", ignore.eval = FALSE)
# plot(routes_network, vertex.cex = 3)
```

```{r}
# p <- c(0.001,0.01,0.03,0.05,0.1, 0.15)
# p_names <- c("0.001","0.01","0.03","0.05","0.1", "0.15")
# g <- 2:20
# 
# atleast1 <- function(p,g){1-(1-p)^g}
# exact1 <- function(p,g){p*(1-p)^(g-1)}
# atleast1(0.001, 7)
# exact1(0.001, 7)
# 
# 
# exact_results <- do.call(rbind, lapply(p, exact1, g))
# row.names(exact_results) <- p_names
# colnames(exact_results) <- 2:20
# exact_results <- cbind(exact_results, colnames(exact_results), rownames(exact_results))
# 
# atleast_results <- do.call(rbind, lapply(p, atleast1, g))
# row.names(atleast_results) <- p_names
# colnames(atleast_results) <- 2:20
# atleast_results <- matrix(atleast_results, dimnames=list(t(outer(colnames(atleast_results), rownames(atleast_results), FUN=paste)), NULL))
# 
# 
# 
# 
# ggplot() +
#   geom_line(allci_corr_indiv, mapping = aes(x=pool, y=tp/(tp + fn), color=as.factor(prevalence), linetype = corr_type)) +
#   geom_line(allci_uncorr_sub, mapping = aes(x=pool, y=tp/(tp + fn), color=as.factor(prevalence), linetype = corr_type)) +
#   facet_wrap(vars(factor(allci_corr_indiv$above.llod, labels=c("5% samples Ct>LoD","10% samples Ct>LoD","15% samples Ct>LoD","20% samples Ct>LoD","25% samples Ct>LoD","30% samples Ct>LoD")))) +
#   theme_bw() + 
#   scale_color_brewer(palette="RdYlBu", name="Prevalence") + 
#   xlab("Pool size") + ylab("Expected positive percent agreement") +
#   ggtitle("Correlated Individuals") +
#   scale_x_continuous(limits=c(1,20), breaks=seq(0,20,2)) + scale_y_continuous(limits=c(0.75,1),breaks=seq(0.75,1,.1)) +
#   guides(color=guide_legend(title="Proportion of\ntests positive")) + 
#   guides(linetype=guide_legend(title="Correlation Structure")) 
```

```{r}
pool.max <- 20
sim_probs <- read.csv("sim_probs_.1.2.csv")
sim_probs[,1] <- NULL
probs_dat <- rbindlist(lapply(2:pool.max, function (p) { # pool size
  rbindlist(lapply(c(0.001,0.01,0.03,0.05,0.1), function(prevalence) { # proportion positive tests 
    rbindlist(lapply(0:p, function(positives) { # number of positives
      
      if (positives == 0) {
        data.frame(
          pool=p, 
          pos=positives, 
          prevalence=prevalence, 
          prob_sim = (1-prevalence)^p,
          prob_bin = dbinom(positives, p, prevalence))
      } 
      else {
        data.frame(
          pool=p,
          pos=positives,
          prevalence=prevalence,
          # probability = dbinom(positives, p, prevalence)/n,
          prob_sim = (1-(1-prevalence)^p)*sim_probs[positives, (p-1)], 
          prob_bin = dbinom(positives, p, prevalence))
      }
    }))
  }))
}))

colourCount <- length(unique(probs_dat$pos))
myColors <- colorRampPalette(brewer.pal(9, "Set1"))(colourCount)

# ggplot() +
#   geom_line(probs_dat, mapping = aes(x=pool, y=probability, color=as.factor(pos))) +
#   facet_wrap(vars(factor(probs_dat$prevalence, labels=c("0.001","0.01","0.03","0.05","0.1")))) +
#   theme_bw() +
#   scale_fill_manual(values = myColors, name="Prevalence") +
#   xlab("Pool size") + ylab("Probability") +
#   ggtitle("Simulated probability of k positives given prevalence and pool size") +
#   scale_x_continuous(limits=c(1,20), breaks=seq(0,20,2)) + scale_y_continuous(limits=c(0,1),breaks=seq(0,1,.1)) +
#   guides(color=guide_legend(title="Number of\ntests positive"))

ggplot(probs_dat, mapping = aes(x=pool, y=prob_sim, fill=as.factor(pos))) +
  geom_bar(position = "stack", stat = "identity") +
  facet_wrap(vars(factor(probs_dat$prevalence, labels=c("Prevalence = 0.001","0.01","0.03","0.05","0.1")))) +
  theme_bw() +
  scale_fill_manual(values = myColors, name="Number of\ntests positive") +
  xlab("Pool size") + ylab("Probability") +
  ggtitle("Simulated probability of k positives given prevalence and pool size") +
  scale_x_continuous(limits=c(0,21), breaks=seq(0,21,2)) + scale_y_continuous(limits=c(0,1.01),breaks=seq(0,2,.1))

ggplot(probs_dat, mapping = aes(x=pool, y=prob_bin, fill=as.factor(pos))) +
  geom_bar(position = "stack", stat = "identity") +
  facet_wrap(vars(factor(probs_dat$prevalence, labels=c("0.001","0.01","0.03","0.05","0.1")))) +
  theme_bw() +
  scale_fill_manual(values = myColors, name="Number of\ntests positive") +
  xlab("Pool size") + ylab("Probability") +
  ggtitle("Binomial probability of k positives given prevalence and pool size") +
  scale_x_continuous(limits=c(0,21), breaks=seq(0,21,2)) + scale_y_continuous(limits=c(0,1.01),breaks=seq(0,2,.1)) 

# probs_dat[probs_dat$prevalence == 0.1 & probs_dat$pos == 0, ]

```





