---
title: "Simulating Probabilities of Positive Pools"
output: pdf_document
---

Objective: to simulate P(k positives | group size) in networks / communities of correlated individuals. 

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(network)
library(ggplot2)
library(dplyr)
library(data.table)
library(RColorBrewer)
```


# P(K positives | 1 infectious individual in network)
GIVEN that there is an infected individual in the network, what is the probability that k other people are infected? 
This loop simulates propagation through household given there is an infected individual. Does NOT account for individuals becoming infected by outside prevalence (network transmission ONLY).

```{r}
group_max <- 20 # maximum group size
n <- 100000 # number of repetitions of simulation
# fxn to calculate p(k positives | group size, prevalence)
calc_probs1 <- function(N, min, max){ # N = group size, prev = prevalence
  # create nodes
  nodes <- tibble(id = 1:N)
  
  # Create edges 
  from <- rep(1:N, each = (N-1))
  to <- unlist(lapply(1:N, function(x) setdiff(1:N, x)))
  
  
  infector <- numeric(n) # initial infectious individual in network
  infected <- matrix(nrow = n, ncol = (N-1)) # secondary infected individuals
  dimnames(infected) <- list(1:n, c(1:(N-1)))
  
  for (i in 1:n){
  # generate matrix of transmission probabilities 
  # household transmission- based on literature: 
  # Secondary infection rate = 53% (95% confidence interval [CI] = 46%–60%)
  Sigma <- matrix(runif(N^2, min, max), nrow = N, ncol = N) # generate random values from .1 to 0.9
  Sigma = 0.5 * (Sigma + t(Sigma)) # make matrix symmetrical 
  diag(Sigma)= rep(1,N) # 1's on diagonal 
  
  transmission_prob <- as.vector(Sigma)[Sigma != 1] # list of transmission probabilities, removing diagonals
  
  edges <- as.data.frame(cbind(from, to, transmission_prob)) 
    # choose starting infected individual
    infector[i] <- sample(nodes$id, 1)
    # infected[i,infector[i]] <- 1 # infector 
    infect_contact <- edges[edges$from == infector[i],] 
    infected[i,] <- unlist(lapply(infect_contact$transmission_prob, function(x) x > runif(1, min = 0, max = 1)))
      # infected if contact rate > uniform(0,1)
    }
  
  # store probability of sum(x)=k positives for given group size
  probs <- c(unlist(lapply(0:(N-1), function(x) sum(rowSums(infected) == x)/n)), rep(0, group_max - N))
  return(probs)
}

```

```{r}
sim_probs_house <- matrix(unlist(lapply(2:20, calc_probs1, min = 0.4, max= 0.6)), nrow = (group_max), ncol = (group_max-1))
dimnames(sim_probs_house) <- list(1:group_max, 2:group_max) 
# rows = total number of infections (1: (group size)), columns = group size
write.csv(sim_probs_house,"sim_probs_.4.6.csv")
# write.csv(sim_probs_house,"sim_probs_house.csv")
```

```{r}
sim_probs_.1.2 <- matrix(unlist(lapply(2:20, calc_probs1, min = 0.1, max= 0.2)),
                         nrow = (group_max),
                         ncol = (group_max-1))
dimnames(sim_probs_.1.2) <- list(1:group_max, 2:group_max) 
# rows = total number of infections (1: (group size)), columns = group size
write.csv(sim_probs_.1.2,"sim_probs_.1.2.csv")
```

# Correlated Individuals
Now we want to allow individuals in the network to be infected either by the outside community (probability = prevalence) or by a single starting infectious individual in the network. "MCMC_sim.R" contains the function that allows us to calculate this. 
```{r}
source("MCMC_sim.R")
pool.max <- 20
sim_probs_test <- read.csv("sim_probs_.1.2.csv")
sim_probs_test[,1] <- NULL

probs_dat <- rbindlist(lapply(2:pool.max, function (p) { # pool size
  rbindlist(lapply(c(0.001,0.01,0.03,0.05,0.1), function(prevalence) { # proportion positive tests 
    sim_probs = calc_probs(p, prevalence,min=0.1, max=0.2)
    rbindlist(lapply(0:p, function(positives) { # number of positives
      
      if (positives == 0) {
        data.frame(
          pool=p, 
          pos=positives, 
          prevalence=prevalence, 
          prob_sim = sim_probs[which(sim_probs$n == 0), "Freq"],
          prob_test = (1-prevalence)^p, # network transmission only 
          prob_bin = dbinom(positives, p, prevalence))
      } 
      else {
        data.frame(
          pool=p,
          pos=positives,
          prevalence=prevalence,
          # probability = dbinom(positives, p, prevalence)/n,
          prob_sim = sim_probs[which(sim_probs$n == positives), "Freq"], 
          prob_test = (1-(1-prevalence)^p)*sim_probs_test[positives, (p-1)], # network transmission only 
          prob_bin = dbinom(positives, p, prevalence))
      }
    }))
  }))
}))

write.csv(probs_dat, "probs_dat.csv")

# test <- read.csv("probs_dat.csv")
```

Plot the results using the different methods. 
```{r}
colourCount <- length(unique(probs_dat$pos))
myColors <- colorRampPalette(brewer.pal(9, "Set1"))(colourCount)

pdf("plot.simprobs_network_community.pdf",width=8, height=5)
ggplot(probs_dat, mapping = aes(x=pool, y=prob_sim, fill=as.factor(pos))) +
  geom_bar(position = "stack", stat = "identity") +
  facet_wrap(vars(factor(probs_dat$prevalence, labels=c("Prevalence = 0.001","0.01","0.03","0.05","0.1")))) +
  theme_bw() +
  scale_fill_manual(values = myColors, name="Number of\ntests positive") +
  xlab("Pool size") + ylab("Probability") +
  ggtitle("Simulated P(k positives | prevalence, pool size) (network & community transmission)") +
  scale_x_continuous(limits=c(0,21), breaks=seq(0,21,2)) + scale_y_continuous(limits=c(0,1.01),breaks=seq(0,2,.1))
dev.off()

pdf("plot.simprobs_binomial.pdf",width=8, height=5)
ggplot(probs_dat, mapping = aes(x=pool, y=prob_bin, fill=as.factor(pos))) +
  geom_bar(position = "stack", stat = "identity") +
  facet_wrap(vars(factor(probs_dat$prevalence, labels=c("0.001","0.01","0.03","0.05","0.1")))) +
  theme_bw() +
  scale_fill_manual(values = myColors, name="Number of\ntests positive") +
  xlab("Pool size") + ylab("Probability") +
  ggtitle("Binomial P(k positives | prevalence, pool size)") +
  scale_x_continuous(limits=c(0,21), breaks=seq(0,21,2)) + scale_y_continuous(limits=c(0,1.01),breaks=seq(0,2,.1)) 
dev.off()

pdf("plot.simprobs_network_only.pdf",width=8, height=5)
ggplot(probs_dat, mapping = aes(x=pool, y=prob_test, fill=as.factor(pos))) +
  geom_bar(position = "stack", stat = "identity") +
  facet_wrap(vars(factor(probs_dat$prevalence, labels=c("0.001","0.01","0.03","0.05","0.1")))) +
  theme_bw() +
  scale_fill_manual(values = myColors, name="Number of\ntests positive") +
  xlab("Pool size") + ylab("Probability") +
  ggtitle("Simulated P(k positives | prevalence, pool size) (network only transmission)") +
  scale_x_continuous(limits=c(0,21), breaks=seq(0,21,2)) + scale_y_continuous(limits=c(0,1.01),breaks=seq(0,2,.1)) 
dev.off()
# probs_dat[probs_dat$prevalence == 0.1 & probs_dat$pos == 0, ]

```


```{r}
# check: probabilities should sum to 1 
probs_dat %>%
  group_by(pool, prevalence) %>%
  summarise_all(sum)

```
# "Realistic" Scenario
Simulate probabilities uisng a more realistic scenario where groups are populated with a mixture of correlated and uncorrelated individuals. The MCMC.R script contains the function simulate_infections() that simulates these probabilities, taking the arguments nb_group (number of correlated individuals), nb_out (number of uncorrelated individuals), Sigma (correlation matrix), prev (prevalence vector), B (number of simulation repetitions, default B=1000)
```{r}
source("MCMC.R") # contains simulate_infections() fxn
pool.max <- 20

probs_dat2 <- rbindlist(lapply(1:pool.max, function (p) { # pool size
  # number of correlated individuals, number of uncorrelated individuals
  nb_group <- trunc(.5*p)
  nb_out <- p - nb_group
   # create correlation matrix (function of number of correlated individuals)
  Sigma <- matrix(runif(p^2, 0.1, 0.2), nrow = p, ncol = p) # generate random values from .1 to 0.9
  Sigma = 0.5 * (Sigma + t(Sigma)) # make matrix symmetrical
  diag(Sigma)= rep(1,p) # 1's on diagonal
  
  rbindlist(lapply(c(0.001,0.01,0.03,0.05,0.1), function(prevalence) { # proportion positive tests 
    prev <- runif(p, .25*prevalence, 4*prevalence)
    sim_probs_real = simulate_infections(nb_group, nb_out, Sigma, prev)
    rbindlist(lapply(0:p, function(positives) { # number of positives
      
      if (positives == 0) {
        data.frame(
          pool=p, 
          pos=positives, 
          prevalence=prevalence, 
          prob_sim_real = sim_probs_real[which(sim_probs_real$n == 0), "Freq"])
      } 
      else {
        data.frame(
          pool=p,
          pos=positives,
          prevalence=prevalence,
          # probability = dbinom(positives, p, prevalence)/n,
          prob_sim_real = sim_probs_real[which(sim_probs_real$n == positives), "Freq"])
      }
    }))
  }))
}))


write.csv(probs_dat2, "probs_dat_real.csv")
# check 
probs_dat2 %>%
  group_by(pool, prevalence) %>%
  summarise_all(sum)
```

```{r}
colourCount <- length(unique(probs_dat2$pos))
myColors <- colorRampPalette(brewer.pal(9, "Set1"))(colourCount)

pdf("plot.simprobs_real.pdf",width=8, height=5)
ggplot(probs_dat2, mapping = aes(x=pool, y=prob_sim_real, fill=as.factor(pos))) +
  geom_bar(position = "stack", stat = "identity") +
  facet_wrap(vars(factor(probs_dat2$prevalence, labels=c("Prevalence = 0.001","0.01","0.03","0.05","0.1")))) +
  theme_bw() +
  scale_fill_manual(values = myColors, name="Number of\ntests positive") +
  xlab("Pool size") + ylab("Probability") +
  ggtitle("Simulated P(k positives | prevalence, pool size) for 'Realistic' Scenario") +
  scale_x_continuous(limits=c(0,21), breaks=seq(0,21,2)) + scale_y_continuous(limits=c(0,1.01),breaks=seq(0,2,.1))
dev.off()
```


# P(K positives | group size, prevalence)
This loop simulates the probability that someone becomes infected at all, and then the probability that the infection propogates through the network. 
```{r}
# group_max <- 20 # maximum group size
# n <- 1000 # number of repetitions of simulation
# 
# # fxn to calculate p(k positives | group size, prevalence)
# calc_probs <- function(N, prev){ # N = group size, prev = prevalence
# 
#   # create nodes
#   nodes <- tibble(id = 1:N)
#   
#   # Create edges 
#   from <- rep(1:N, each = (N-1))
#   to <- unlist(lapply(1:N, function(x) setdiff(1:N, x)))
#   
#   # generate matrix of random transmission probabilities 
#   # replace with values from the literature 
#   Sigma <- matrix(runif(N^2, 0.1, 0.9), nrow = N, ncol = N) # generate random values from .1 to 0.9
#   Sigma = 0.5 * (Sigma + t(Sigma)) # make matrix symmetrical 
#   diag(Sigma)= rep(1,N) # 1's on diagonal 
# 
#   transmission_prob <- as.vector(Sigma)[Sigma != 1] # list of transmission probabilities, removing diagonals
#   
#   edges <- as.data.frame(cbind(from, to, transmission_prob)) 
#   
#   infector <- numeric(n)
#   infected <- matrix(nrow = n, ncol = N)
#   dimnames(infected) <- list(1:n, c(1:N))
#   v_long <- rep(1:10, each = 2)
#   v <- v_long[1:N]
#   # prev <- 0.01
#   risk_probs <- prev*v
#   
#   for (i in 1:n){
#     
#     # flip coin to decide if anyone is infected
#     flip <- rbinom(1, 1, prob = (1-exp(sum(log(1-risk_probs)))))
#     # remove this line - assume someone is infected 
#     
#     if (flip == 0) { # nobody infected
#       infected[i,] <- 0
#     } 
#     else{ # flip = 1 -> transmit infection
#       infector[i] <- which(rmultinom(1, size = 1, prob= (v/sum(v))) > 0) 
#       infected[i,infector[i]] <- 1 # infector 
#       infect_contact <- edges[edges$from == infector[i],] 
#       infected[i,-infector[i]] <- unlist(lapply(infect_contact$transmission_prob, function(x) x > runif(1, min = 0, max = 1)))
#       # infected if contact rate > uniform(0,1)
#     }
#   }
#   
#   # store probability of sum(x)=k positives for given group size
#   probs <- c(unlist(lapply(0:N, function(x) sum(rowSums(infected) == x)/n)), rep(0, group_max - N))
#   return(probs)
# }
# 
# results_prev_01 <- matrix(unlist(lapply(1:20, calc_probs, prev = 0.01)), nrow = (group_max + 1), ncol = group_max)
# dimnames(results_prev_01) <- list(0:group_max, 1:group_max) # rows = number positives (0: group size), columns = group size
```



